---
title: "Developing Data Products Course Project"
output: ioslides_presentation
author: "Zhiyu Lu"
date: '2022-11-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)

```

## Introduction

Here, we create the graphs showing how diamonds are priced depend on not only the number of carat, but their cut, color, and clarity.

* **Cut:** Quality of the diamonds (Ideal, Premium, Very Good, Good, Fair).

* **Color:** Colour of diamonds from the best to the worst (D, E, F, G, H, I).

* **Clarity:** Measurement of how clear the diamond is from the best to the worst (IF, VVS2, VVS1, VS2, VS1, SI2, SI1, I1).

## Overview

* The application is written in Shiny, a web application framework for R.

* The source code consists of two files: server.R and ui.R.

* server.R includes the backend of a Shiny web application.

* ui.R includes the the user-interface elements.

* The application is hosted on Rstudio’s shiny server.

## Documentation

Here is the summary of the dataset "diamonds", which includes approximately 5000 cases.

```{r, echo=FALSE}
data(diamonds)
plot(diamonds[,c(1:4,7)])
```

## Try the App

Use the Shiny app at

<https://zhiyulu.shinyapps.io/Developing_Data_Products_Course_Project/>

Get the app source code at

<https://github.com/ZhiYLu/Developing_Data_Products_Course_Project/upload/main>
